---
title: "CS130 Final Project"
author: "Aida Mazyte, Chiffon Nguyen"
date: "December 15, 2023"
output:
  html_document:
    toc: yes
    toc_depth: '2'
    df_print: paged
  pdf_document:
    toc: yes
    toc_depth: 2
    number_sections: yes
    keep_tex: no
    df_print: paged
    highlight: tango
editor_options:
  markdown:
    wrap: 72
---
# Introduction 

Replication for the 2021 paper "Philadelphia’s Excise Tax on Sugar-Sweetened and Artificially Sweetened Beverages and Supplemental Nutrition Assistance Program Benefit Redemption" by Benjamin W. Chrisinger. 

# [O] Clean data

Set up

```{r libraries, message=FALSE, warning=FALSE}
rm(list = ls())

libraries_to_install <- c("knitr", "dplyr", "readr", "reshape2", "lubridate", 
                          "GGally", "Synth", "foreach", "doParallel")

# Check if each library is already installed, and install it if not
libraries_not_installed <- libraries_to_install[
  !sapply(libraries_to_install, requireNamespace, quietly = TRUE)]

if (length(libraries_not_installed) > 0) {
  install.packages(libraries_not_installed, dependencies = TRUE)
}

# Check if the libraries are successfully loaded
if (!all(sapply(libraries_to_install, requireNamespace, quietly = TRUE))) {
  message("Some libraries failed to load. Switch to manual installation")
}

library(readr)
library(dplyr)
library(lubridate)
library(doParallel)

# Set up parallel processing
cl <- makeCluster(detectCores()-2)
registerDoParallel(cl)
```

Read data, skip columns 1-2

```{r read_data, message=FALSE, warning=FALSE}
d0 = read_csv("final_dataset.csv", col_select = 3:13)
str(d0)
```

From the original paper code: 

1. Rearrange the data by year in the ascending order (2005-2019). 
2. Make sure every year has two data points: in January and July 
3. Create a `time` counter: 1 for Jan 2005, 2 for July 2005, 3 for Jan 2006, etc. This will be used as the `time.variable` for synthetic control

```{r data_time}

# Make sure every year has two data points: in January and July
d0 = d0[month(as.Date(paste0(d0$Date,"-01"))) %in% c(1,7),]
d0 = d0[d0$Year>=2005 & d0$Year<=2019,]
d0 = d0[!d0$Date %in% c("2019-01"),]

posttreat.last.halfyear = length(unique(d0$Date)) # 29
pretreat.last.halfyear = length(unique(d0[d0$Year<2017,]$Date)) # 24

# Create time reference table (Date & time counter)
timekey = data.frame(Date=names(table(unique(d0$Date))),
                     time=seq(1:posttreat.last.halfyear))

# Left merge
d0 = merge(d0, timekey, by="Date", all.x=TRUE, sort = TRUE)
```

Turn data into more readable format

```{r data_time_read}
timekey$half.year <- format(as.Date(paste0(timekey$Date, "-01")), "%b %Y")
```

Remove counties with missing values under columns `Snap.Benefits.USDA` and `Snap.Individuals.USDA`

```{r}
d0 = d0[!d0$county_state %in% 
          unique(d0[is.na(d0$Snap.Benefits.USDA),]$county_state),]
d0 = d0[!d0$county_state %in% 
          unique(d0[is.na(d0$Snap.Individuals.USDA),]$county_state),]
d0 = d0[!d0$county_state %in% 
          unique(d0[is.na(d0$Unemployment.Rate),]$county_state),]
```

Transform some predictor variables to log scale

```{r data_log}
d0$log.Redemption.Amt = log(d0$Redemption.Amt)
d0$log.Snap.Individuals.USDA = log(d0$Snap.Individuals.USDA)
d0$log.Snap.Benefits.USDA = log(d0$Snap.Benefits.USDA)
d0$log.Authorized.Stores = log(d0$Authorized.Stores)
d0$log.population.5yr = log(d0$population.5yr)
```

Add the outcome for SNAP redemption per participant

```{r data_outcome}
d0$Redemption.Amt.PC = d0$Redemption.Amt / d0$Snap.Individuals.USDA
```

Change the unemployment rate from `double` (fraction) to `numeric`
```{r data_type}
d0$Unemployment.Rate = as.numeric(d0$Unemployment.Rate)
```

Remove counties that have been found to exhibit strange high/low cycles,
spikes, and other anomalies in outcome or predictor variables

```{r data_abnormal}
d0 = d0[!d0$county_state %in% c("Ventura County, CA", 
                                 "Santa Barbara County, CA", 
                                 "Monterey County, CA", 
                                 "Horry County, SC",
                                 "Tulsa County, OK",
                                 "Fresno County, CA",
                                 "New Castle County, DE",
                                 "Stark County, OH",
                                 "Baltimore County, MD",
                                 "Kern County, CA",
                                 "Williamson County, TX",
                                 "Cook County, IL"),]
```

Remove counties without complete data (only include counties with two
data points per year)

```{r data_complete}
# new dataframe counts of each unique value in the county_state column 
n_obs = data.frame(table(d0$county_state))

# include only counties with complete data 
complete = unique(n_obs[n_obs$Freq==posttreat.last.halfyear,]$Var1)
d0 = d0[d0$county_state %in% complete,]
```

Reassign county ID

```{r data_id}
newid = data.frame(county_state=unique(d0$county_state),
                   id = seq_len(length(unique(d0$county_state))))
d0 = merge(d0, newid, by="county_state")
d0$county_id = d0$id
d0 = d0 %>%
  arrange(id, time)
```

# Synthetic Control Setup

## [O] Filter similar counties

Package the code from the original paper into a function:

1.  Compute median values for predictor variables
2.  For two different time periods (pre-2012 and 2012-2015), compute the
    intercept and slope of the linear regression model for the logarithm
    of Redemption.Amt over time.
3.  Identify counties whose slope of SNAP redemption is within a certain
    range of the treatment county's slope
4.  Select counties whose predictor variables are within certain ranges
    of the treatment county's averages

```{r}

study.counties = c("Philadelphia County, PA", "Montgomery County, PA", 
                   "Delaware County, PA", "Bucks County, PA")

get_similar_counties <- function(
    d, treatment.county, span1=1.25, span2=1.25, span3=5) {
  
  # Step 0: Remove neighbors
  neighbors.to.remove = setdiff(study.counties, treatment.county)
  d = d[!d$county_state %in% neighbors.to.remove, ]
  
  # Step 1: Compute median values for predictor variables 
  pred_avgs = d[d$time < pretreat.last.halfyear, ] %>%
    group_by(county_state) %>%
    summarise(
      Authorized.Stores = median(Authorized.Stores, na.rm = TRUE),
      Unemployment.Rate = median(Unemployment.Rate, na.rm = TRUE),
      Snap.Individuals.USDA = median(Snap.Individuals.USDA, na.rm = TRUE),
      Snap.Benefits.USDA = median(Snap.Benefits.USDA, na.rm = TRUE),
      population.5yr = median(population.5yr, na.rm = TRUE)
    )

  treat_avgs = pred_avgs[pred_avgs$county_state == treatment.county, ]

  # Step 2.1: Compute the intercept and slope of the linear regression Pre-2012
  slope_avgs.1 = d[d$Year < 2012, ] %>%
    group_by(county_state) %>%
    do({
      mod = lm(log.Redemption.Amt ~ time, data = .)
      data.frame(Intercept = coef(mod)[1], Slope = coef(mod)[2])
    })

  treat_avgs.1 = slope_avgs.1[slope_avgs.1$county_state == treatment.county, ]

  # Step 2.2: Compute the intercept and slope of the linear regression 2012-2015
  slope_avgs.2 = d[d$Year >= 2012 & d$Year <= 2015, ] %>%
    group_by(county_state) %>%
    do({
      mod = lm(log.Redemption.Amt ~ time, data = .)
      data.frame(Intercept = coef(mod)[1], Slope = coef(mod)[2])
    })

  treat_avgs.2 = slope_avgs.2[slope_avgs.2$county_state == treatment.county, ]

  # Step 3:  Identify counties whose slope of SNAP redemption is within 
  # a certain range of the treatment county's slope
  preds.1 = slope_avgs.1[
    (slope_avgs.1$Slope < treat_avgs.1$Slope * span1 &
       slope_avgs.1$Slope > treat_avgs.1$Slope * (1 / span1)), ]$county_state

  preds.2 = if (treat_avgs.2$Slope > 0) {
    slope_avgs.2[(slope_avgs.2$Slope < treat_avgs.2$Slope * span2 &
                    slope_avgs.2$Slope > treat_avgs.2$Slope * (1 / span2)), ]$county_state
  } else {
    slope_avgs.2[(slope_avgs.2$Slope > treat_avgs.2$Slope * span2 &
                    slope_avgs.2$Slope < treat_avgs.2$Slope * (1 / span2)), ]$county_state
  }

  # Step 4: Select counties based on proximity of predictor variables 
  # with treatment county
  preds.3 = pred_avgs[
    (pred_avgs$Authorized.Stores < treat_avgs$Authorized.Stores * span3 &
       pred_avgs$Authorized.Stores > treat_avgs$Authorized.Stores * (1 / span3) &
       pred_avgs$Unemployment.Rate < treat_avgs$Unemployment.Rate + span3 &
       pred_avgs$Unemployment.Rate > treat_avgs$Unemployment.Rate - span3 &
       pred_avgs$Snap.Individuals.USDA < 
          treat_avgs$Snap.Individuals.USDA * span3 &
       pred_avgs$Snap.Individuals.USDA > 
          treat_avgs$Snap.Individuals.USDA * (1 / span3) &
       pred_avgs$Snap.Benefits.USDA < treat_avgs$Snap.Benefits.USDA * span3 &
       pred_avgs$Snap.Benefits.USDA > treat_avgs$Snap.Benefits.USDA * (1 / span3) &
       pred_avgs$population.5yr < treat_avgs$population.5yr * span3 &
       pred_avgs$population.5yr > treat_avgs$population.5yr * (1 / span3)
    ), ]$county_state

  # Remove counties predictors that aren't close to the treatment county
  d_filtered = d[(d$county_state %in% preds.1 &
                    d$county_state %in% preds.2 &
                    d$county_state %in% preds.3), ]

  return(d_filtered)
}
```

Set up a dataframe for counties only. There are 2702 counties in the raw
donor pool.

```{r}
donor_pool = data.frame(county_id = unique(d0$county_id),
                        county_state = unique(d0$county_state))
nrow(donor_pool)
```

## [D] Check missing values among predictors 
```{r}
colSums(is.na(d0))
```

## [D] Check multicollinearity between predictors 

This is an extra step that the author didn't perform in the paper. We need to ensure that the matrix involved in the calculations for synthetic control is invertible, by avoiding perfect multicollinearity among the predictors.

In short, we try to find out predictors that are highly correlated.

```{r message=FALSE, warning=FALSE}
library(GGally)

vars <- c("Unemployment.Rate",  
          "log.Redemption.Amt",
          "Redemption.Amt.PC",
          "log.Snap.Individuals.USDA", 
          "log.Snap.Benefits.USDA",
          "log.Authorized.Stores", 
          "log.population.5yr")

# exclude NAs when calculate pairwise Pearson's correlation
ggcorr(d0[, vars], use = "pairwise.complete.obs", palette = "RdYlBu") +
  ggtitle("Correlation Heatmap")
```
`log.Redemtion.Amt` is almost perfectly correlated with `log.population.5yr` and `log.Authorized.Stores`. `log.population.5yr` and `log.Authorized.Stores` are also highly correlated.

In this case, `log.population.5yr` should not be used as a predictor at any time.

## [D] Run synthetic control
```{r synth_total, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(Synth)

set.seed(1)

run_synth_total <- function(treatment.county) {
  # Step 1: Get Similar Counties
  d = get_similar_counties(
    d0, 
    treatment.county = treatment.county,
    span1 = 3, span2 = 3, span3 = 7
  )
  
  # Step 2: Get Identifier of Treatment and Control Units
  j = donor_pool %>%
    filter(county_state == treatment.county) %>%
    select(county_id) %>%
    pull()
  controlunits = setdiff(unique(d$id), j)
  
  # Step 3: Dataprep
  dataprep.out <- dataprep(
    foo = d,
    predictors    = c("Unemployment.Rate", 
                      "log.Authorized.Stores",
                      "log.Snap.Individuals.USDA", 
                      "log.Snap.Benefits.USDA"), 
    dependent     = "log.Redemption.Amt",
    special.predictors = list(
      list("log.Redemption.Amt", seq(from = 2, to = 2, by = 1), "mean"),
      list("log.Redemption.Amt", seq(from = 4, to = 4, by = 1), "mean"),
      list("log.Redemption.Amt", seq(from = 6, to = 6, by = 1), "mean"),
      list("log.Redemption.Amt", seq(from = 8, to = 8, by = 1), "mean"),
      list("log.Redemption.Amt", seq(from = 10, to = 10, by = 1), "mean"),
      list("log.Redemption.Amt", seq(from = 12, to = 12, by = 1), "mean"),
      list("log.Redemption.Amt", seq(from = 14, to = 14, by = 1), "mean"),
      list("log.Redemption.Amt", seq(from = 16, to = 16, by = 1), "mean"),
      list("log.Redemption.Amt", seq(from = 18, to = 18, by = 1), "mean"),
      list("log.Redemption.Amt", seq(from = 20, to = 20, by = 1), "mean"),
      list("log.Redemption.Amt", seq(from = 22, to = 22, by = 1), "mean"),
      list("log.Redemption.Amt", seq(from = 24, to = 24, by = 1), "mean")),
    unit.variable = "id",
    time.variable = "time",
    treatment.identifier = j,
    controls.identifier = controlunits,
    time.predictors.prior = 1:pretreat.last.halfyear,
    time.optimize.ssr = 1:pretreat.last.halfyear,
    unit.names.variable = "county_state",
    time.plot = 1:posttreat.last.halfyear)
  
  # Step 4: Synthetic control
  synth.out <- synth(
    data.prep.obj = dataprep.out,
    optimxmethod = c("CG", "L-BFGS-B", "nlm", "nlminb", "spg", "ucminf"),
    quadopt = "ipop")
  
  # Return the results as a list
  return(list(dataprep.out = dataprep.out, synth.out = synth.out))
}
```


# Figure 2 Replication

## Figure 2a. Total SNAP Redemption

Run synthetic control to get the gaps (treated - control)
```{r gaps_total, message=FALSE, warning=FALSE, include=FALSE}
library(reshape2)

gaps <- tibble(half.year = timekey$Date)
dataprep.out.list <- list()
synth.out.list <- list()

for (county.name in study.counties) {
  # Get first 4 letters of full county_name
  county <- substr(county.name, 1, 4)
  
  # Run synthetic control
  synth.results <- run_synth_total(county.name)
  
  # Save dataprep.out and synth.out
  dataprep.out.list[[county]] <- synth.results$dataprep.out
  synth.out.list[[county]] <- synth.results$synth.out
  
  # Get the log outcome (treat county & synthetic control)
  logY1 = synth.results$dataprep.out$Y1plot
  logY0 = synth.results$dataprep.out$Y0plot
  weights = synth.results$synth.out$solution.w
  
  # Calculate the gap between treated and control
  # log-scaled to normal scale to million dollars
  gap_mil = as.numeric((exp(logY1) - (exp(logY0) %*% weights)) / 1e7)
  
  gaps = mutate(gaps, !!county := gap_mil)
}

# Reshape the data to long form to plot
gaps.to.plot <- melt(gaps, 
                    id.vars = "half.year",
                    variable.name = "county", 
                    value.name = "gap.redemption.million")
```

Plot the gaps

```{r fig2a}
library(ggplot2)

# Figure 2a
ggplot(gaps.to.plot, aes(x = half.year, 
                         y = gap.redemption.million, 
                         color = county,
                         group = county,
                         shape = county)) +
  geom_line(linewidth = 0.5, linetype = 1) +
  geom_point(size = 2) + 
  geom_hline(yintercept = 0, linetype = "dashed") + 
  geom_vline(xintercept = "2017-01", linetype = "dashed", color = "black") +
  labs(title = "2a. Gaps in SNAP Redemption for 4 counties",
       x = "Date",
       y = "Gaps in SNAP Redemption ($ Million)",
       color = NULL,
       shape = NULL) +
  scale_x_discrete(labels = timekey$half.year) +
  scale_y_continuous(breaks = seq(-1, 3, 0.5)) +
  scale_color_manual(values = c("Phil" = "gray3", 
                                "Buck" = "orange", 
                                "Dela" = "blue", 
                                "Mont" = "limegreen"),
                     labels = c("Phil" = "Philadelphia County",
                                "Buck" = "Bucks County",
                                "Dela" = "Delaware County",
                                "Mont" = "Montgomery County")) +
  scale_shape_manual(values = c("Phil" = 15, "Buck" = 16, "Dela" = 18, "Mont" = 17),
                     labels = c("Phil" = "Philadelphia County",
                                "Buck" = "Bucks County",
                                "Dela" = "Delaware County",
                                "Mont" = "Montgomery County")) +
  theme_classic() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-label ticks
    panel.border = element_blank(),      # Remove panel border
    legend.position = c(0.02, 0.99),  # Adjust legend position
    legend.justification = c(0, 1),   # Adjust legend justification
    legend.box.background = element_rect(color = "black"),  # Border around legend
    legend.text = element_text(size=8),
    legend.key.size = unit(0.5, 'cm'), 
    legend.key.height = unit(0.3, 'cm'), 
    legend.key.width = unit(1, 'cm')
  )
```

## Figure 2b. SNAP Redemption Per Participant

```{r synth_perperson, message=FALSE, warning=FALSE, include=FALSE}

# SAME CONFIGURATION AS AUTHOR's 5a
run_synth_per_participant <- function(treatment.county) {
  # Step 1: Get Similar Counties
  d = get_similar_counties(
    d0, 
    treatment.county = treatment.county,
    span1 = 3, span2 = 3, span3 = 7
  )
  
  # Step 2: Get Identifier of Treatment and Control Units
  j = donor_pool %>%
    filter(county_state == treatment.county) %>%
    select(county_id) %>%
    pull()
  controlunits = setdiff(unique(d$id), j)
  
  # Step 3: Dataprep
  dataprep.out <- dataprep(
    foo = d,
    predictors    = c("Unemployment.Rate", 
                      "log.Authorized.Stores",
                      "log.Snap.Individuals.USDA", 
                      "log.Snap.Benefits.USDA"), 
    dependent     = "Redemption.Amt.PC",
    special.predictors = list(
        list("Redemption.Amt.PC", seq(from = 2, to = 2, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 4, to = 4, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 6, to = 6, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 8, to = 8, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 10, to = 10, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 12, to = 12, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 14, to = 14, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 16, to = 16, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 18, to = 18, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 20, to = 20, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 22, to = 22, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 24, to = 24, by = 1), "mean")),
    unit.variable = "id",
    time.variable = "time",
    treatment.identifier = j,
    controls.identifier = controlunits,
    time.predictors.prior = 1:pretreat.last.halfyear,
    time.optimize.ssr = 1:pretreat.last.halfyear,
    unit.names.variable = "county_state",
    time.plot = 1:posttreat.last.halfyear)
  
  # Step 4: Synthetic control
  synth.out <- synth(
    data.prep.obj = dataprep.out,
    optimxmethod = c("DEoptC", "malschains", "nlminb")
    )
  
  # Return the results as a list
  return(list(dataprep.out = dataprep.out, synth.out = synth.out))
}
```

Run synthetic control to get the gaps (treated - control)
```{r gaps, message=FALSE, warning=FALSE, include=FALSE}

pc.gaps <- tibble(half.year = timekey$Date)
pc.dataprep.out.list <- list()
pc.synth.out.list <- list()

for (county.name in study.counties) {
  # Get first 4 letters of full county_name
  county <- substr(county.name, 1, 4)
  
  # Run synthetic control
  synth.results <- run_synth_per_participant(county.name)
  
  # Save dataprep.out and synth.out
  pc.dataprep.out.list[[county]] <- synth.results$dataprep.out
  pc.synth.out.list[[county]] <- synth.results$synth.out
  
  # Get the outcome per participant (treat county & synthetic control)
  Y1 = synth.results$dataprep.out$Y1plot
  Y0 = synth.results$dataprep.out$Y0plot
  weights = synth.results$synth.out$solution.w
  
  # Calculate the gap between treated and control per participant (in dollars)
  gap_mil = as.numeric(Y1 - Y0 %*% weights) 
  
  pc.gaps = mutate(pc.gaps, !!county := gap_mil)
}
```

```{r}
# Reshape the data to long form to plot
pcgaps.to.plot <- melt(pc.gaps, 
                    id.vars = "half.year",
                    variable.name = "county", 
                    value.name = "pc.gap.redemption")
```

Plot the gaps

```{r fig2b, message=FALSE, warning=FALSE}
# Figure 2b
ggplot(pcgaps.to.plot, aes(x = half.year, 
                         y = pc.gap.redemption, 
                         color = county,
                         group = county,
                         shape = county)) +
  geom_line(linewidth = 0.5, linetype = 1) +
  geom_point(size = 2) + 
  geom_hline(yintercept = 0, linetype = "dashed") + 
  geom_vline(xintercept = "2017-01", linetype = "dashed", color = "black") +
  labs(title = "2b. Gaps in SNAP Redemption Per Participant for 4 counties",
       x = "Date",
       y = "Gaps in SNAP Redemption ($)",
       color = NULL,
       shape = NULL) +
  scale_x_discrete(labels = timekey$half.year) +
  scale_y_continuous(breaks = seq(-10, 60, 10)) +
  scale_color_manual(values = c("Phil" = "gray3", 
                                "Buck" = "orange", 
                                "Dela" = "blue", 
                                "Mont" = "limegreen"),
                     labels = c("Phil" = "Philadelphia County",
                                "Buck" = "Bucks County",
                                "Dela" = "Delaware County",
                                "Mont" = "Montgomery County")) +
  scale_shape_manual(values = c("Phil" = 15, "Buck" = 16, 
                                "Dela" = 18, "Mont" = 17),
                     labels = c("Phil" = "Philadelphia County",
                                "Buck" = "Bucks County",
                                "Dela" = "Delaware County",
                                "Mont" = "Montgomery County")) +
  theme_classic() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-label ticks
    panel.border = element_blank(),      # Remove panel border
    legend.position = c(0.02, 0.99),  # Adjust legend position
    legend.justification = c(0, 1),   # Adjust legend justification
    legend.box.background = element_rect(color = "black"),  
    legend.text = element_text(size=8),
    legend.key.size = unit(0.5, 'cm'), 
    legend.key.height = unit(0.3, 'cm'), 
    legend.key.width = unit(1, 'cm')
  )
# ggsave("fig2b.png")
```

# Extension: Leave-one-out Robustness Check

```{r loo_func, message=FALSE, warning=FALSE, include=FALSE}
library(foreach)

global_vars <- c("d0", "donor_pool", "timekey",
                 "pretreat.last.halfyear", "posttreat.last.halfyear")

# Export global variables to the parallel workers
clusterExport(cl, global_vars)

# Modify the synthetic control functions
loo_synth_per_participant <- function(treatment.county) {
  # Step 1: Get Similar Counties
  d = get_similar_counties(
    d0, 
    treatment.county = treatment.county,
    span1 = 3, span2 = 3, span3 = 7
  )
  
  # Step 2: Get Identifier of Treatment and Control Units
  j = donor_pool %>%
    filter(county_state == treatment.county) %>%
    select(county_id) %>%
    pull()
  controlunits = setdiff(unique(d$id), j)
  
  # Create an empty ... to store the gaps
  loo.gaps <- data.frame()
  
  # Iterate over each control unit for leave-one-out
  loo.gaps <- foreach(control_unit = controlunits, .combine = rbind, 
                      .packages = "Synth") %dopar% {
    
    # Step 3: Dataprep for the current leave-one-out iteration
    dataprep.out <- dataprep(
      foo = d[d$id != control_unit, ],  # Exclude the current control unit
      predictors = c("Unemployment.Rate", 
                     "log.Authorized.Stores",
                     "log.Snap.Individuals.USDA", 
                     "log.Snap.Benefits.USDA"), 
      dependent = "Redemption.Amt.PC",
      special.predictors = list(
        list("Redemption.Amt.PC", seq(from = 2, to = 2, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 4, to = 4, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 6, to = 6, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 8, to = 8, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 10, to = 10, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 12, to = 12, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 14, to = 14, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 16, to = 16, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 18, to = 18, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 20, to = 20, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 22, to = 22, by = 1), "mean"),
        list("Redemption.Amt.PC", seq(from = 24, to = 24, by = 1), "mean")),
      unit.variable = "id",
      time.variable = "time",
      treatment.identifier = j,
      controls.identifier = setdiff(controlunits, control_unit),
      time.predictors.prior = 1:pretreat.last.halfyear,
      time.optimize.ssr = 1:pretreat.last.halfyear,
      unit.names.variable = "county_state",
      time.plot = 1:posttreat.last.halfyear)
    
    # Step 4: Synthetic control for the current leave-one-out iteration
    synth.out <- synth(
      data.prep.obj = dataprep.out,
      optimxmethod = c("DEoptC", "malschains", "nlminb"),
      quadopt = "ipop"
    )
    
    # Store current gap between treated and control
    gap <- as.numeric(
      dataprep.out$Y1plot - (dataprep.out$Y0plot %*% synth.out$solution.w)
    )

    # Store in loo.gaps
    data.frame(
      half.year = timekey$Date,
      county = as.character(control_unit), 
      gap = gap)
  }
  
  # Return the list of results for all leave-one-out iterations
  return(loo.gaps)
}

# loo.bucks = loo_synth_per_participant("Bucks County, PA")
```

```{r}
loo.phil = loo_synth_per_participant("Philadelphia County, PA")
loo.dela = loo_synth_per_participant("Delaware County, PA")
loo.mont = loo_synth_per_participant("Montgomery County, PA")

```

```{r loo_run, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

loo.gaps.list <- list()

for (county.name in study.counties) {
  # Get first 4 letters of full county_name
  county <- substr(county.name, 1, 4)
  
  # Run leave-one-out on the current county
  loo.gaps <- loo_synth_per_participant(county.name)
  
  # Add loo.gaps to loo.gaps.list by "county"
  loo.gaps.list[[county]] = loo.gaps
}

# Stop parallel processing
stopCluster(cl)
```

## Philadelphia
```{r}
ggplot(loo.phil, aes(x = half.year, y = gap, group = county)) +
  geom_line(linewidth = 0.5, linetype = 1, color = "gray") +
  geom_point(size = 1, color = "gray") + 
  geom_line(data = pcgaps.to.plot[pcgaps.to.plot$county == "Phil", ], 
            aes(x = half.year, y = pc.gap.redemption), 
            linetype = 1, color = "black", size = 1) +  # Add the new line
  geom_hline(yintercept = 0, linetype = "dashed") + 
  geom_vline(xintercept = "2017-01", linetype = "dashed", color = "black") +
  labs(title = "Leave-one-out Analysis for Philadelphia
       SNAP Redemption per participant", 
       x = "Date",
       y = "Gaps in SNAP Redemption ($)") +
  scale_x_discrete(labels = timekey$half.year) +
  theme_classic() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-label ticks
    panel.border = element_blank(),      # Remove panel border
  )
```

## Delaware
```{r}
ggplot(loo.dela, aes(x = half.year, y = gap, group = county)) +
  geom_line(linewidth = 0.5, linetype = 1, color = "gray") +
  geom_point(size = 1, color = "gray") + 
  geom_line(data = pcgaps.to.plot[pcgaps.to.plot$county == "Dela", ], 
            aes(x = half.year, y = pc.gap.redemption), 
            linetype = 1, color = "black", size = 1) +  # Add the new line
  geom_hline(yintercept = 0, linetype = "dashed") + 
  geom_vline(xintercept = "2017-01", linetype = "dashed", color = "black") +
    labs(title = "Leave-one-out Analysis for Delaware
       SNAP Redemption per participant", 
       x = "Date",
       y = "Gaps in SNAP Redemption ($)") +
  scale_x_discrete(labels = timekey$half.year) +
  theme_classic() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-label ticks
    panel.border = element_blank(),      # Remove panel border
  )
```

## Montgomery
```{r}
ggplot(loo.mont, aes(x = half.year, y = gap, group = county)) +
  geom_line(linewidth = 0.5, linetype = 1, color = "gray") +
  geom_point(size = 1, color = "gray") + 
  geom_line(data = pcgaps.to.plot[pcgaps.to.plot$county == "Mont", ], 
            aes(x = half.year, y = pc.gap.redemption), 
            linetype = 1, color = "black", size = 1) +  # Add the new line
  geom_hline(yintercept = 0, linetype = "dashed") + 
  geom_vline(xintercept = "2017-01", linetype = "dashed", color = "black") +
    labs(title = "Leave-one-out Analysis for Montgomery
       SNAP Redemption per participant", 
       x = "Date",
       y = "Gaps in SNAP Redemption ($)") +
  scale_x_discrete(labels = timekey$half.year) +
  theme_classic() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-label ticks
    panel.border = element_blank(),      # Remove panel border
  )
```

## Bucks